%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Tom Marty} \\ \vspace{1pt}
        \href{https://3rdcore.github.io/}{\underline{https://3rdcore.github.io}}  $|$     \href{mailto:x@x.com}{\underline{tom.marty@mila.quebec}} $|$ 
    Montreal, Canada
    
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
        \resumeSubheading
      {MILA - Montréal Institute of Learning Algorithms}{Jan. 2024 -- }
      {Ph.D. in Machine Learning}{Montréal, Canada}
      \vspace{.2pt}
      \begin{itemize}
          \item \textbf{Courses :} Causal Inference (Dhanya Sridhar)
      \end{itemize}
      \resumeSubheading
      {Polytechnique Montréal}{Sep. 2021 -- Jun. 2023}
      {M.Sc. in Operationnal Research - GPA 3.91}{Montréal Canada}
      \vspace{.2pt}
      \begin{itemize}
          \item \textbf{Courses :} Représentation Learning (Aaron Courville) $|$ Spectral Graph Theory (Guy Wolf) $|$ Continual Learning (Irina Rish)  
          \item \textbf{\href{https://github.com/corail-research/SeaPearl.jl}{SeaPearl} (Thesis) - Supervised by Quentin Cappart and Louis-Martin Rousseau:} Using RL and Graph Representation Learning to accelerate discrete optimization problem solving process - paper accepted at \textbf{CP 2023}
      \end{itemize}
    \resumeSubheading
      {Ecole Polytechnique - X 2018}{Sep. 2018 -- Jun. 2021}
      {Bachelor Of Science in Computer Science, Minor in Applied Mathematics - GPA 3.84}{Palaiseau, France}
      \vspace{.2pt}
      \begin{itemize}
          \item \textbf{Theoretical Computer Science} : Graph Theory $|$ Computational Geometry $|$ Advanced Algorithmic
          \item \textbf{Applied Mathematics} : Optimisation $|$ Statistical modeling $|$ Deep Learning
          \item \textbf{Computer Graphics} : Computer Vision $|$ Image Processing and Rendering
      \end{itemize}
    \resumeSubheading
      {Lycée Jean-Baptiste Say}{Sep. 2016 -- Jun. 2018}
      {"Classe préparatoire" Intensive multi-disciplinary program leading to entrance exams - GPA 4.00}{Paris, France} 
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
      \resumeSubheading
      {Visiting Researcher}{Apr. 2023 -- Sept. 2023}
      {\href{https://corail-research.github.io/}{ServiceNow Research}}{Montréal, Canada}
    \resumeItemListStart
        \resumeItem{Developped WebArena : an open-source Benchmark and Gym environment for evaluating Agent at solving tasks on a Web Browser}
        \resumeItem{Workshop paper accepted at NeurIPS 2023 FMDM Workshop. One paper under review at ICML 2024.}
      \resumeItemListEnd
      \resumeSubheading
      {Research Supervisor}{Jan. 2022 -- Sept. 2022}
      {\href{https://corail-research.github.io/}{Corail Research Group}}{Montréal, Canada}
    \resumeItemListStart
        \resumeItem{Supervised five interns on the development of the open-source project \href{https://github.com/corail-research/SeaPearl.jl}{SeaPearl}}
        \resumeItem{Teaching Assistant for the course \href{https://www.polymtl.ca/programmes/cours/intelligence-artif-methodes-et-algorithmes}{INF8215} given by Quentin Cappart in Fall 21 and Fall 22 }
      \resumeItemListEnd
    \resumeSubheading
      {Research Engineer Intern}{Jan. 2021 -- Sept. 2021}
      {\href{https://corail-research.github.io/}{Corail Research Group}}{Montréal, Canada}
    \resumeItemListStart
        \resumeItem{Developped {\textit{SeaPearl}} : an open-source RL-driven generic Constraint Programming solver}
        \resumeItem{Used Deep Q-networks and Heterogeneous GNNs to approximate optimal decision process}
    \resumeItemListEnd
    \resumeSubheading
      {Software Engineer Intern}{Jun. 2020 -- Sept. 2020}
      {Dronisos, drone light show company}{Bordeaux, France}
      \resumeItemListStart
        \resumeItem{Developed \textit{Harmony}, a Physics based meta-heuristic that secures massive drone swarms ( NP-Complete ) }
                \resumeItem{\textit{Harmony} - currently in use - reduced the allocated securing time from 2 weeks (handmade) to 2 seconds}
        \resumeItem{Achieved automatic securing on the company first 1000 drones choreography (+500k\$ show)}
      \resumeItemListEnd
      
    \resumeSubheading
      {Teaching Assistant}{Nov. 2018 -- Mar. 2019}
      {Ministry of National Education}{Noyon, France}
      \resumeItemListStart
        \resumeItem{Responsible for a group of up to 20 undergraduate students during scientific workshops}
        \resumeItem{Worked alongside the academic team to prepare students for entrance exams}

    \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
        \resumeProjectHeading
          {\textbf{WebArena : an Open-Source Benchmark for evaluating Web Agents} $|$ \emph{Python}}{Apr. 2023 -- Sept. 2023}
          \resumeItemListStart
            \resumeItem{\href{https://scholar.google.com/citations?view_op=view_citation&hl=fr&user=-YXor_wAAAAJ&citation_for_view=-YXor_wAAAAJ:UeHWp8X0CEIC}{Workshop paper} accepted at NeurIPS 2023 FMDM Workshop, New Orleans}
            \resumeItem{Paper under review at ICML 2024}

          \resumeItemListEnd
        \resumeProjectHeading
          {\textbf{SeaPearl : an Open-Source RL-driven Constraint-Programming Solver } $|$ \emph{Julia}}{Fev. 2021 -- Jul. 2023}
          \resumeItemListStart
            \resumeItem{\href{https://scholar.google.com/citations?view_op=view_citation&hl=fr&user=-YXor_wAAAAJ&citation_for_view=-YXor_wAAAAJ:2osOgNQ5qMEC}{Paper} accepted at CP2023, Toronto}
            \resumeItem{Visit \href{https://3rdcore.github.io/SeaPearl.html}{this link} for detailed explanations}
            
          \resumeItemListEnd
            \resumeProjectHeading
          {\textbf{Adversarial Attacks on Sentiment Classification models }$|$ \emph{Python, HuggingFace}}{Fev. 2022 -- May. 2022}
          \resumeItemListStart
            \resumeItem{Adversarial fine-tunning on large NLP models : \href{https://www.eleuther.ai/}{Eleuther AI} GPT 125M/1.3B/2.7B/6B parameters}
            \resumeItem{Evidence of a correlation between scaling and robustness against increasingly subtle Adversarial Attacks}
            \resumeItem{Project coordinated by Irina Rish, AI CIFAR Chair holder, MILA}

          \resumeItemListEnd
                      \resumeProjectHeading
          {\textbf{Diffusion Geodesic distance for non-linear dimensionality reduction }$|$ \emph{Python}}{Oct. 2021 -- Jan. 2022}
          \resumeItemListStart
            \resumeItem{Approximated the geodesic distance using a diffusion process over the manifold}
            \resumeItem{Proposed a new data visualization algorithm based on Multi-Dimentionnal Scaling and Diffusion Geodesic}


          \resumeItemListEnd
          	\resumeProjectHeading
          {\textbf{Autonomous Drone Swarm Deployment - DGA contest }$|$ \emph{Python, PyTorch}}{Nov. 2020 -- Mar. 2021}
          \resumeItemListStart
            \resumeItem{Multi-agent Q-Learning method for deployment optimization }
            \resumeItem{ Density-Based Spatial Clustering for point of interest detection}
          \resumeItemListEnd
          
          \resumeProjectHeading
          {\textbf{Realtime 3D Deep Motion Capture} $|$ \emph{C++, OpenCV, PyTorch}}{Oct. 2020 -- Dec. 2020}
          \resumeItemListStart
            \resumeItem{Implemented a method of inferring a full character's 3d pose using only  a camera as an input}
            \resumeItem{Used a EECV 2020 research paper to implement the algorithm}
            
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Sketch-based Shape Retrieval} $|$ \emph{Python, C++, OpenGL}}{Sep. 2020 -- Dec. 2020}
          \resumeItemListStart
            \resumeItem{Implemented a method to find any specific 3d model in a database using a drawing as an input}
            \resumeItem{Succeeded to faithfully retrieve several simple 3D shapes by using a single drawing given by a user}

          \resumeItemListEnd
	
    \resumeSubHeadingListEnd




%-----------Hobbies-----------
\section{Student Association}
 \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Public Speaking Club: Rethorix} }{Oct. 2019 -- Oct. 2020}
          \resumeItemListStart
            \resumeItem{Organization of an eloquence contest between the schools of the Plateau de Saclay}

          \resumeItemListEnd
               \resumeProjectHeading
          {\textbf{President of Nuit du Styx} }{Nov. 2020}
          \resumeItemListStart
            \resumeItem{General organization and logistic of an electronic music festival gathering more than 2000 peoples}

          \resumeItemListEnd
    \resumeSubHeadingListEnd
%-------------------------------------------
%
%-----------PROGRAMMING SKILLS-----------
\section{Skills \& Hobbies}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    \textbf{Languages}{: French : Native $|$ English : Fluent $|$ Russian : Primary } \\
     \textbf{Programming Languages}{: Python, Julia, C++, R} \\
     \textbf{Developer Tools}{: Git, SLURM, Pytorch, Lightning, Hydra, SCRUM, VScode, Pytest} \\
    }
    \textbf{Open-Source web service deployment}{: Nextcloud, Nginx, Swag, OpenMediaVault}\\
    \textbf{Remote Controlled UAV}{: Conception, Building, Programmation, Testing, Adjustment } \\
     \textbf{Sports}{: Outdoor climbing, River surf, Ski, Montain hiking } \\}
 \end{itemize}
 
\end{document}
